\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}

Facing the large quantity and variety of information on the Internet nowadays, was created the necessity of the existence of systems that help the users to find what they look for according to their preferences, this way reducing the time wasted in researching within this environment. Looking around e-commerce websites, for example, there are hundreds or thousands of products on display for the users, making it hard to find a product that corresponds to the clients' desires. The following work discusses the development of a real estate recommendation system, in the context of a B2B type of business, by means of an e-commerce website for real estate sales for housing companies displaying their properties and receive visibility from their possible clients, using a recommendation system that would serve them more efficiently and decreasing the research efforts for something that could suit their interests for the acquisition of a new property. The main goal is to help clients that visit said website to find the desired property more easily, developing a more powerful recommendation system compared to existing systems. The recommendations will be based on the characteristics of these clients acquired by the recommendation system. It will follow a hybrid approach, that is, contemplating two or more research techniques, generating better results for customers using this system. An initial study was conducted through bibliographical research on concepts, approaches and techniques used in real estate recommendation systems to generate a new system proposal that will be presented in this work.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Key-words}: machine learning. reccomender system. e-commerce. real estate.
 \end{otherlanguage*}
\end{resumo}
